Solving two-person zero-sum sequential games via efficient computation of Nash equilibria: proof-of-concept on Kuhn's 3-card Poker

### 2014-10-30 neurobreakfast.tex
new files

%\logo{\includegraphics[scale=0.1]{img/logo_parietal.png}}
\begin{frame}
  \frametitle{Problem}
  Given a \textcolor{orange}{sequential two-person zero-sum game} (e.g Texas Hold'em Poker), construct an \textcolor{orange}{optimal player}.
  %% Approximate the population covariance matrix $\Sigma$ from $n$ samples.
  %% \begin{itemize}
  %% \item $\B{S}$ is the $p \times p$ sample covariance
  %%   matrix.\\
  %%   $\B{S} = \frac{1}{n}\sum^n_{i=1}x_ix_i\trans$. $\mathbb{E}[S] = \Sigma$.
  %% \item Largest (resp. smallest) eigenvalue of $S$ is biased upwards
  %%   (resp. downwards)
  %% \item $\Rightarrow$ Shrinkage: pushing up (resp. pulling down) the
  %%   largest (resp. smallest) eigenvalue. \textcolor{gray}{(Stein
  %%     1976)}.
  %% \end{itemize}

@@

\begin{frame}
\frametitle{Strategy profiles, simplexes and complexes}
\begin{definition}
  \begin{itemize}[<+->]
    \item The \textcolor{blue}{$n$-\textit{simplex}}, denoted $\Delta_n$, is the subset of $\mathbb{R}^{n+1}$ defined by
      \begin{equation}
        \Delta_n := \left\{x \in \mathbb{R}^{n+1}\text{ }|\text{ } x_i \ge 0\text{ } \forall i, \text{ and } \sum_{i=1}^{n+1}{x_i} = 1\right\}
      \end{equation}
    \item Each kink $\delta_i := (0, ..., 0,1,0, ...,0)$ of $\Delta_n$ represents a \textit{\textcolor{blue}{pure-strategy}}.
      Any non-kink point $x$ of $\Delta_n$ represents a
      \textit{\textcolor{blue}{mixed-strategy}}. Thus $\Delta_n$ is simply the \textit{convex hall} of $(n+1)$-dimensional pure strategies $\delta_i$.
    \item A \textit{\textcolor{blue}{complex}} is an abstract \textit{\textcolor{blue}{polyhedron}} whose kinks are themselves simplexes. Points on
      a complex correspond to \textit{\textcolor{blue}{behavioural strategies}}.
  \end{itemize}
\end{definition}
\end{frame}

\begin{frame}
\frametitle{Simplexes and complexes (examples of)}
%% \begin{figure}
%%   \includegraphics[width=3cm]{simplex.png}
%%   \includegraphics[width=3cm]{7-simplex.png}
%%   \includegraphics[width=3cm]{10-simplex.png}
%%   \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
%% \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Sequences and payoff matrix}
  \begin{itemize}[<+->]
    \item Let $S_p$ be the sequences of moves for player $p$. Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
      \item Precisely,
        \begin{equation}
          S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
        \end{equation}
        \item The payoff matrix $A = (a_{\sigma,\tau})$ by
          \begin{equation}
            a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
            \end{equation}
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: Why? How?}

  \begin{itemize}
  \item ($p/n$ large) or ($\Sigma$ eigenvalues close to one another)
    $\Rightarrow$ linear shrinkage OK.\\($p/n$ small) or ($\Sigma$
    eigenvalues dispersed) $\Rightarrow$ non-linear shrinkage better.
  \item Mar\v{c}enko-Pastur equation: relationship between $\B{S}$ and
    $\B{\Sigma}$ eigenvalues under large-dimensional asymptotics.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: deeper into the "how?"}

  \begin{itemize}
  \item $H_n$ empirical d.f. of sample ($\B{S}_n$) eigenvalues $\B{\tau}_n$.\\
    $H_n(\B{\tau}) \equiv
    \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{[\tau_i,+\infty[}(\tau)$
  \item $F_n$ e.d.f. of population ($\B{\Sigma}_n$) eigenvalues
    $\B{\lambda}_n$.\\$\B{Y}_n = \B{X}_n\B{\Sigma}^{1/2}_n$, $\B{X}_n
    \sim \mathcal{N}(\B{0},\text{Id})$
  \item $F_n$ (resp. $H_n$) converges almost surely to $F$ (resp. $H$).
  \item Stieltjes transform of a non-decreasing function $G$:
     $\forall z \in \mathbb{C}^+, m_G(z) \equiv
     \int^{+\infty}_{-\infty}\frac{1}{u - z}dG(u)$
   \item Mar\v{c}enko-Pastur equation: $\forall z \in \mathbb{C}^+,
     m_F(z) = \int^{+\infty}_{-\infty}\frac{1}{\tau[1-\frac{p}{n}-\frac{p}{n}zm_F(z)] - z}dH(\tau)$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Non-Linear Ledoit-Wolf: Implementation\ldots}

  \begin{equation*}
    \begin{split}
      \textcolor{red}{Q_{n,p}}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
              & \B{t} \equiv (t_1,\ldots,t_p)\trans
              \mapsto Q_{n,p}(\B{t}) \equiv
              (q^1_{n,p}(t),\ldots,q^p_{n,p}(t))\trans
    \end{split}
  \end{equation*}

  \vfill
  \hrule{}
  \vfill

  $\textcolor{blue}{\hat{\B{\tau}}_n} = \underset{\B{t} \in [0, \infty[^p}{\text{argmin}} 
      \frac{1}{p} \sum^p_{i=1}[\textcolor{red}{q^i_{n,p}(}\B{t}\textcolor{red}{)} - \lambda_{n,i}]^2$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)} \simeq \frac{n-p}{p\lambda_i} - \frac{n}{p}\frac{1}{\textcolor{blue}{\hat{\B{\tau}}_{n,i}}\lambda_i}$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{purple}{\hat{d}_i^*} = \frac{\lambda_i}{|1 - \frac{p}{n} - \frac{p}{n}|^2\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)}}$; {\scriptsize Covariance:} $S_n^*\B{U}_n\textcolor{purple}{\hat{\B{D}}^*_n}\B{U}_n\trans${\scriptsize , with }$\B{S}_n=\B{U}_n\B{D}_n\B{U}_n\trans$

\end{frame}

\begin{frame}
  \frametitle{About the $Q_{n,p}$ function}

  \begin{equation*}
    \begin{split}
      Q_{n,p}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
              & \B{t} \equiv (t_1,\ldots,t_p)\trans
              \mapsto Q_{n,p}(\B{t}) \equiv
              (\textcolor{red}{q^1_{n,p}(}t\textcolor{red}{)},\ldots,\textcolor{red}{q^p_{n,p}(}t\textcolor{red}{)})\trans
    \end{split}
  \end{equation*}

  \vfill
  \hrule{}
  \vfill

  $\forall i = 1, \ldots, p \quad \textcolor{red}{q^i_{n,p}(}t\textcolor{red}{)} \equiv
  p\int_{(i-1)/p}^{i/p}\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)}du$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)} \equiv \sup\{x \in \mathbb{R}: \textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \leq u\}$

  \vfill
  \hrule{}
  \vfill

  $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \max \left\{1 - \frac{n}{p}, \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{\{t_i = 0\}}\right\}$ if $x = 0$, $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \underset{\eta \rightarrow 0^+}{\lim}\frac{1}{\pi}\int^{+\infty}_{-\infty}\text{Im}\left[\textcolor{purple}{m^{\B{t}}_{n,p}(}\zeta + i\,\eta\textcolor{purple}{)}\right]d\zeta$ otherwise

  \vfill
  \hrule{}
  \vfill

  $m \equiv \textcolor{purple}{m^{\B{t}}_{n,p}(}z\textcolor{purple}{)}$ sol. in $\left\{m \in \mathbb{C}: -\frac{n-p}{nz} + \frac{p}{n}\right\}$ of $\textcolor{purple}{m} = \frac{1}{p}\sum^p_{i=1}\frac{1}{t_i(1 - \frac{p}{n} - \frac{p}{n}z\textcolor{purple}{m}) - z}$

\end{frame}

>>>>

\begin{frame}
\frametitle{Some necessary history ...}
\begin{itemize}[<+->]
  \item Blaise Pascal, and other giants ($\sim 1623$)...
    \item Zemelo 1913 (subgame perfect equilibrium, backward induction)
    \item Von Neumann and Oskar Morgenstern (Cooperative Games, \textit{Theory of Games and Economic Behavior, 1944}),
    \item John F. Nash (Non-cooperative games, Nash Equilibrium)
    \item L. Shapley (concept of value for bargaining games, etc.),
    \item Tucker, Kuhn, and co. (equivalence between LCP and problem of computation of Nash Equilibria;
      subgame perfect equilibrium again).
\end{itemize}
\end{frame}

%\logo{\includegraphics[scale=0.1]{img/logo_parietal.png}}
\begin{frame}
  \frametitle{Problem}
  Given a \textcolor{orange}{sequential two-person zero-sum game} (e.g Texas Hold'em Poker), construct an \textcolor{orange}{optimal player}.

  %% Approximate the population covariance matrix $\Sigma$ from $n$ samples.
  %% \begin{itemize}
  %% \item $\B{S}$ is the $p \times p$ sample covariance
  %%   matrix.\\
  %%   $\B{S} = \frac{1}{n}\sum^n_{i=1}x_ix_i\trans$. $\mathbb{E}[S] = \Sigma$.
  %% \item Largest (resp. smallest) eigenvalue of $S$ is biased upwards
  %%   (resp. downwards)
  %% \item $\Rightarrow$ Shrinkage: pushing up (resp. pulling down) the
  %%   largest (resp. smallest) eigenvalue. \textcolor{gray}{(Stein
  %%     1976)}.
  %% \end{itemize}

@@

@@

%% \begin{frame}
%%   \frametitle{Game tree (T) for Kuhn's 3-card Poker}
%%       \begin{figure}
%%         \includegraphics[width=12cm]{Kuhn3112_gt.png}
%%       \end{figure}
%% \end{frame}

\begin{frame}
\frametitle{Strategy profiles, simplexes and complexes}
\begin{definition}
  \begin{itemize}[<+->]
    \item The \textcolor{blue}{$n$-\textit{simplex}}, denoted $\Delta_n$, is the subset of $\mathbb{R}^{n+1}$ defined by
      \begin{equation}
        \Delta_n := \left\{x \in \mathbb{R}^{n+1}\text{ }|\text{ } x_i \ge 0\text{ } \forall i, \text{ and } \sum_{i=1}^{n+1}{x_i} = 1\right\}
      \end{equation}
    \item Each kink $\delta_i := (0, ..., 0,1,0, ...,0)$ of $\Delta_n$ represents a \textit{\textcolor{blue}{pure-strategy}}.
      Any non-kink point $x$ of $\Delta_n$ represents a
      \textit{\textcolor{blue}{mixed-strategy}}. Thus $\Delta_n$ is simply the \textit{convex hall} of $(n+1)$-dimensional pure strategies $\delta_i$.
    \item A \textit{\textcolor{blue}{complex}} is an abstract \textit{\textcolor{blue}{polyhedron}} whose kinks are themselves simplexes. Points on
      a complex correspond to \textit{\textcolor{blue}{realization plans}}.
  \end{itemize}
\end{definition}
\end{frame}

\begin{frame}
\frametitle{Simplexes and complexes (examples of)}
\begin{figure}
  \includegraphics[width=3cm]{simplex.png}
  \includegraphics[width=3cm]{7-simplex.png}
  \includegraphics[width=3cm]{10-simplex.png}
  \caption{\textbf{Left}: 2-simplex \textbf{Middle}: 7-simplex \textbf{Right}: 10-simplex}
\end{figure}
\end{frame}

\begin{frame}
  \frametitle{Sequences and payoff matrix}
  \begin{definition}
    Given a node $t \in V(T)$, and a player $p \in \{0, 1, 2\}$, let $\sigma_p(t)$ be the sequence of player $p$'s moves along the path from the root node \ to $t$.
\end{definition}

  \begin{itemize}[<+->]
    \item Let $S_p$ be the sequences of moves for player $p$. Then any $\sigma \in S_p$ is either the empty sequence $\empty$ set or can be written as $\sigma_{h_p} c$ where $h_p$ is an information set of $p$ and $c$ is a choice at $h_p$.
    \item Precisely,
      \begin{equation}
        S_p = \{\emptyset\} \cup \{\sigma_{h}c\text{ }|\text{ }h \in H_{p}, c \in C_h\}
        \end{equation}
\item The payoff matrix $A = (a_{\sigma,\tau})$ by
  \begin{equation}
    a_{\sigma,\tau} := \sum_{\text{leaf }t:\text{ } \sigma_1(t) = \sigma, \sigma_2(t) = \tau}\beta_0(\sigma_0(t))a(t)
  \end{equation}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Example of sequence-form representation}
  \begin{itemize}[<+->]
    \item \textcolor{blue}{$S_1 = [[],[(\{'chance': ('A',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(B,2)')],
 [(\{'chance': ('A',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(F,3)')],
 [(\{'chance': ('K',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(B,2)')],
 [(\{'chance': ('K',), 'choices': ('(B,2)', '(F,3)'), 'sigma': ''\}, '(F,3)')]]$}
\item \textcolor{green}{$I_1 = \{(('A',), '', ('(B,2)', '(F,3)')): ['(/,0).(w,1)', '(/,0).(x,1)'],
  (('K',), '', ('(B,2)', '(F,3)')): ['(/,0).(u,1)', '(/,0).(v,1)']\}$}
\item \textcolor{red}{$E = \left( \begin{array}{ccccc}
    1&0&0&0&0\\-1&1&1&0&0\\-1&0&0&1&1
    \end{array} \right)$,
$e=(1, 0, 0)$,
$A = \left( \begin{array}{ccccc}
0&0&0&0&0\\0&0&0&1&0\\0&0&0&0&0\\0&-1&0&0&0\\0&0&0&0&0
\end{array}\right)$
}
\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Kuhn's Poker sequence-form representation}
  \[   E = \left( \begin{array}{ccccccccccccc}
1&0&0&0&0&0&0&0&0&0&0&0&0\\-1&0&0&0&0&0&0&0&0&1&0&0&1\\-1&1&0&0&1&0&0&0&0&0&0&0&0\\-1&0&0&0&0&1&0&0&1&0&0&0&0\\0&-1&1&1&0&0&0&0&0&0&0&0&0\\0&0&0&0&0&-1&1&1&0&0&0&0&0\\0&0&0&0&0&0&0&0&0&-1&1&1&0
\end{array} \right),\]
  $e = (1, 0, 0, 0, 0, 0, 0)$

@@

\begin{frame}
  \frametitle{Practical considerations}
  In practice, the \textcolor{orange}{payoff matrix $A$ will be very huge} (\textcolor{green}{for example $18 x 10^9$ rows by $18 x 10^9$ columns for Texas Hold'em!}) but \textcolor{blue}{sparse, with a nice block structure}

\begin{equation}
  A = \begin{bmatrix}A_1\text{ }0 \text{ }0\\ 0\text{ }A_2\text{ }0 \\0 \text{ } 0\text{ }A_3\end{bmatrix}
\end{equation}

where (for some ``small'' (worst case $\sim 100$ by $100$) sparse matrices $F_1$, ..., $B_2$, ..., $S$, $W$):
\begin{equation}
  \left .
  \begin{split}
    A_1 := F_1 \otimes B_1\\
    A_2 := F_2 \otimes B_2\\
    A_3 := F_3 \otimes B_3 + S \otimes W,
  \end{split}
  \right\}
\end{equation}
\end{frame}

%% \begin{frame}
%%   \frametitle{Non-Linear Ledoit-Wolf: Why? How?}

%%   \begin{itemize}
%%   \item ($p/n$ large) or ($\Sigma$ eigenvalues close to one another)
%%     $\Rightarrow$ linear shrinkage OK.\\($p/n$ small) or ($\Sigma$
%%     eigenvalues dispersed) $\Rightarrow$ non-linear shrinkage better.
%%   \item Mar\v{c}enko-Pastur equation: relationship between $\B{S}$ and
%%     $\B{\Sigma}$ eigenvalues under large-dimensional asymptotics.
%%   \end{itemize}
%% \end{frame}

%% \begin{frame}
%%   \frametitle{Non-Linear Ledoit-Wolf: deeper into the "how?"}

%%   \begin{itemize}
%%   \item $H_n$ empirical d.f. of sample ($\B{S}_n$) eigenvalues $\B{\tau}_n$.\\
%%     $H_n(\B{\tau}) \equiv
%%     \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{[\tau_i,+\infty[}(\tau)$
%%   \item $F_n$ e.d.f. of population ($\B{\Sigma}_n$) eigenvalues
%%     $\B{\lambda}_n$.\\$\B{Y}_n = \B{X}_n\B{\Sigma}^{1/2}_n$, $\B{X}_n
%%     \sim \mathcal{N}(\B{0},\text{Id})$
%%   \item $F_n$ (resp. $H_n$) converges almost surely to $F$ (resp. $H$).
%%   \item Stieltjes transform of a non-decreasing function $G$:
%%      $\forall z \in \mathbb{C}^+, m_G(z) \equiv
%%      \int^{+\infty}_{-\infty}\frac{1}{u - z}dG(u)$
%%    \item Mar\v{c}enko-Pastur equation: $\forall z \in \mathbb{C}^+,
%%      m_F(z) = \int^{+\infty}_{-\infty}\frac{1}{\tau[1-\frac{p}{n}-\frac{p}{n}zm_F(z)] - z}dH(\tau)$
%%   \end{itemize}
%% \end{frame}

%% \begin{frame}
%%   \frametitle{Non-Linear Ledoit-Wolf: Implementation\ldots}

%%   \begin{equation*}
%%     \begin{split}
%%       \textcolor{red}{Q_{n,p}}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
%%               & \B{t} \equiv (t_1,\ldots,t_p)\trans
%%               \mapsto Q_{n,p}(\B{t}) \equiv
%%               (q^1_{n,p}(t),\ldots,q^p_{n,p}(t))\trans
%%     \end{split}
%%   \end{equation*}

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\textcolor{blue}{\hat{\B{\tau}}_n} = \underset{\B{t} \in [0, \infty[^p}{\text{argmin}} 
%%       \frac{1}{p} \sum^p_{i=1}[\textcolor{red}{q^i_{n,p}(}\B{t}\textcolor{red}{)} - \lambda_{n,i}]^2$

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)} \simeq \frac{n-p}{p\lambda_i} - \frac{n}{p}\frac{1}{\textcolor{blue}{\hat{\B{\tau}}_{n,i}}\lambda_i}$

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\textcolor{purple}{\hat{d}_i^*} = \frac{\lambda_i}{|1 - \frac{p}{n} - \frac{p}{n}|^2\textcolor{PineGreen}{\overset{\smile}{m}^{\hat{\B{\tau}}_n}_{n,p}(}\lambda_i\textcolor{PineGreen}{)}}$; {\scriptsize Covariance:} $S_n^*\B{U}_n\textcolor{purple}{\hat{\B{D}}^*_n}\B{U}_n\trans${\scriptsize , with }$\B{S}_n=\B{U}_n\B{D}_n\B{U}_n\trans$

%% \end{frame}

%% \begin{frame}
%%   \frametitle{About the $Q_{n,p}$ function}

%%   \begin{equation*}
%%     \begin{split}
%%       Q_{n,p}: & [0, \infty[^p \rightarrow [0,\infty[^p \\
%%               & \B{t} \equiv (t_1,\ldots,t_p)\trans
%%               \mapsto Q_{n,p}(\B{t}) \equiv
%%               (\textcolor{red}{q^1_{n,p}(}t\textcolor{red}{)},\ldots,\textcolor{red}{q^p_{n,p}(}t\textcolor{red}{)})\trans
%%     \end{split}
%%   \end{equation*}

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\forall i = 1, \ldots, p \quad \textcolor{red}{q^i_{n,p}(}t\textcolor{red}{)} \equiv
%%   p\int_{(i-1)/p}^{i/p}\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)}du$

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\textcolor{blue}{(F^{\B{t}}_{n,p})^{-1}(}u\textcolor{blue}{)} \equiv \sup\{x \in \mathbb{R}: \textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \leq u\}$

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \max \left\{1 - \frac{n}{p}, \frac{1}{p}\sum^p_{i=1}\mathbb{1}_{\{t_i = 0\}}\right\}$ if $x = 0$, $\textcolor{PineGreen}{F^{\B{t}}_{n,p}(}x\textcolor{PineGreen}{)} \equiv \underset{\eta \rightarrow 0^+}{\lim}\frac{1}{\pi}\int^{+\infty}_{-\infty}\text{Im}\left[\textcolor{purple}{m^{\B{t}}_{n,p}(}\zeta + i\,\eta\textcolor{purple}{)}\right]d\zeta$ otherwise

%%   \vfill
%%   \hrule{}
%%   \vfill

%%   $m \equiv \textcolor{purple}{m^{\B{t}}_{n,p}(}z\textcolor{purple}{)}$ sol. in $\left\{m \in \mathbb{C}: -\frac{n-p}{nz} + \frac{p}{n}\right\}$ of $\textcolor{purple}{m} = \frac{1}{p}\sum^p_{i=1}\frac{1}{t_i(1 - \frac{p}{n} - \frac{p}{n}z\textcolor{purple}{m}) - z}$

%% \end{frame}
